Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-15 Grassmannian_cells.tex
Brief intro to section 4

>>>>

In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_0\subset X_1\subset \cdots \subset X_k=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i-1}$ is isomorphic to an affine space.
